Visually pleasing knot projections

### 2023-02-01 inst/jma_rebuttal_2023_01_30.tex

RE: Why not place nodes at the crossing points? : Yes, this will
require a different, slightly more sophisticated drawing interface;
but this may then pay off heavily in a simpler, more efficient
optimization process.

For each crossing point, the user would see an orthogonal "cross-hair"
that can be shifted and rotated as a whole.  In addition, there are
two parameters (handle-pairs) that control the "velocities" of the two
strands through the crossing.  The optimization routine would
fine-tune these velocities to achieve matching curvature for the two
sequentially connected Bezier curves.

And, yes, if a crossing point falls on a line of mirror symmetry, the
crosshair would automatically be angled at 45 degrees with respect to
this line.  And if the knot has n-fold rotational symmetry, n such
cross hairs would be placed at the vertices of a regular n-gon.  (All
this is not such a "nightmare" if it is properly considered from the
beginning.)

I don't expect that anything in the current system should be changed;
but this approach should definitely be considered in a future version
of such a package.
\textcolor{blue}{\\ This scheme certainly sounds achievable and I have
  alluded to it in the manuscript at the two trefoil knot
  discussion.\\ \\}

@@

Page 6, Line 36: Why ``$\mathbb{R}^{50}$"? - Are there a total of 50
parameters?  What are they?  \textcolor{blue}{\\This was not clear and
  I have rephased.  Old text: ``The optimization typically proceeds
  over $\mathbb{R}^{50}$\ldots". New text: ``The optimization
  proceeds over $\mathbb{R}^n$ where $n$ is the number of parameters
  needed to specify the path; typically $n\gtrsim 50$ for the knots
  presented here".\\ \\}

Page 6, Line 39: ``... the overall bending energy." {\tt ->>} 'minimizing
overall bending energy.'
\textcolor{blue}{\\Fixed\\ \\}

Page 6, Line 42: What is "{\tt > b <}" ?  \textcolor{blue}{\\ This is
  just a detail of standard R syntax.  The first ``{\tt > }" is just
  the R prompt; letter {\tt b} is just a variable; and the symbol
  ``{\tt <-}" usually has a gloss of ``becomes".  Thus {\tt b <- 4} is
  read ``{\tt b} becomes 4". The reason I need a variable is that I
  want to show the result of applying two functions, {\tt
    total\_crossing\_angles()} and {\tt total\_bending\_energy()}, to
  the same variable {\tt b}.\\ \\}

Figures 3 and 5: Try running these figures with only 50 points (and
circles) for each Bezier segment. \textcolor{blue}{\\This is easily
  achievable in the package but the result fails to provide any
  informative or enlightening information.  It simply highlights the
  fact that $n$ was too small.  I show the requested figure below}

\includegraphics[width=13cm]{k7_6_n05.pdf}
% created by knotplot2(k7_6,n=7)

### 2023-02-01 inst/jma_rebuttal_2023_01_30.tex

Page 6, Line 36: Why ``$\mathbb{R}^{50}$"? - Are there a total of 50
parameters?  What are they?  \textcolor{blue}{\\This was not clear and
  I have rephased.  Old text: ``The optimization typically proceeds
  over $\mathbb{R}^{50}$\ldots". New text: ``The optimization
  proceeds over $\mathbb{R}^n$ where $n$ is the number of parameters
  needed to specify the path; typically $n\gtrsim 50$ for the knots
  presented here".\\ \\}

Page 6, Line 39: ``... the overall bending energy." {\tt ->>} 'minimizing
overall bending energy.'
\textcolor{blue}{\\Fixed\\ \\}

Page 6, Line 42: What is "{\tt > b <}" ?  \textcolor{blue}{\\ This is
  just a detail of standard R syntax.  The first ``{\tt > }" is just
  the R prompt; letter {\tt b} is just a variable; and the symbol
  ``{\tt <-}" usually has a gloss of ``becomes".  Thus {\tt b <- 4} is
  read ``{\tt b} becomes 4". The reason I need a variable is that I
  want to show the result of applying two functions, {\tt
    total\_crossing\_angles()} and {\tt total\_bending\_energy()}, to
  the same variable {\tt b}.\\ \\}

Figures 3 and 5: Try running these figures with only 50 points (and
circles) for each Bezier segment. \textcolor{blue}{\\This is easily
  achievable in the package but the result fails to provide any
  informative or enlightening information.  It simply highlights the
  fact that $n$ was too small.  Using $n=50$ is (almost)
  indistinguishable from $n=100$.  I found that $n=100$ represented
  essentially the best visual representation while being
  computationally not too onerous.  I show the requested figure at the
  end (along with $n=7$ and $n=100$ for comparison),
  figures~\ref{7_6_n7}, \ref{7_6_n50}, and \ref{7_6_n100}.  These were
  created with}

\begin{Verbatim}[commandchars=\\\{\}]
\textcolor{blue}{R> pdf(file="k7_6_n07.pdf") ; knotplot2(k7_6,n=7)   ; dev.off()}
\end{Verbatim}
\begin{Verbatim}[commandchars=\\\{\}]
\textcolor{blue}{R> pdf(file="k7_6_n50.pdf") ; knotplot2(k7_6,n=50)  ; dev.off()}
\end{Verbatim}
\begin{Verbatim}[commandchars=\\\{\}]
\textcolor{blue}{R> pdf(file="k7_6_n100.pdf") ; knotplot2(k7_6,n=100) ; dev.off()}
\end{Verbatim}

@@

Page 16, Line 47: ``The strands exert a couple but no force on one
another."  Lengthy discussions should be relegated to the main text,
rather than be in figure captions \textcolor{blue}{\\Done.  This
  discussion is relocated to the main text as suggested.\\ \\}

Figure 14: All the knots are nicer than the ones in Ref [24].  Good
results!\textcolor{blue}{\\Thank you!}

References: Several of them are incomplete and need an URL or a more
detailed description where the source can be found.
\textcolor{blue}{\\Done. \\ \\}

\begin{figure}[h]
  \centering
  \includegraphics[width=10cm]{"k7_6_n07.pdf"}
  \caption{Knot \label{7_6_n7} $7_6$ with $n=7$ nodes per segment}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=10cm]{"k7_6_n50.pdf"}
  \caption{Knot \label{7_6_n50} $7_6$ with $n=50$ nodes per segment}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=10cm]{"k7_6_n100.pdf"}
  \caption{Knot \label{7_6_n100} $7_6$ with $n=100$ nodes per segment}
\end{figure}

### 2023-02-01 inst/jma_knot.tex
issue #81

The knots supplied in the package minimize a weighted sum of these and
other badnesses\footnote{Function {\tt badness()} includes various
``housekeeping'' badnesses which are used to make sure that the
minimum found by {\tt nlm()} is topologically identical to the
starting configuration (a list is given in the Appendix).  Function
{\tt non\_crossing\_strand\_close\_approach\_badness()}, for example,
makes non-crossing strands ``repel'' one another so as not to
introduce spurious intersections.}.  The weightings for the various
badnesses are, of course, subjective; but the system discussed here
allows the user to change the weightings used and compare results.  I
present a short discussion in section~\ref{section_cca} below.
Numerically, the badnesses are evaluated by function {\tt badness()}:

@@

Further work might include adding functionality to deal with links,
although this is not straightforward, and a brief discussion is given
in Appendix B.

@@

\clearpage
\section*{Appendix A: details and motivation for the badness functions}

\section*{Appendix B: some reflections on links}

>>>>

The knots supplied in the package minimize a weighted sum of these and
other badnesses.  Function {\tt badness()} includes various
``housekeeping'' badnesses which are used to make sure that the
minimum found by {\tt nlm()} is topologically identical to the
starting configuration.  Function {\tt
  non\_crossing\_strand\_close\_approach\_badness()}, for example,
makes non-crossing strands ``repel'' one another so as not to
introduce spurious intersections.

\noindent The weightings for the various badnesses are, of course,
subjective; but the system discussed here allows the user to change
the weightings used and compare results.  I present a short discussion
in section~\ref{section_cca} below.  Numerically, the badnesses are
evaluated by function {\tt badness()}:

@@

@@
